\chapter{Introduction}

Supply Chain Simulator (\scs)
is a discrete-event simulation of a three-tier supply chain
with stochastic demand, stochastic lead times, and lost sales.
\scs\ is written in the Java\texttrademark\ programming language.

The supply chain is defined by the topology of the supply chain system,
the demand model, the lead time model,
the shipment schedule
and the inventory replenishment policy.
Next, the user can specify the simulation parameters
such as the initial inventory level
and the number of periods to simulate.
After running the simulation,
\scs\ is able to write as output
statistics of interest
(e.g.\ the service level, average inventory level at the facility)
as well as the raw simulation output.
As \scs\ is designed with a modular software architecture,
the user is able to easily plug-and-play different components
(supply chain topology, demand, lead time, shipment schedule
and inventory replenishment policy).
It is also easy for a user to write a new customized component.
Finally, we explain how to use SCS
to simulate drug distribution in Zambia
and the associated data files which were estimated
using data collected from Zambia.

The raison d'\^{etre} of \scs\
is to evaluate inventory replenishment policies via simulation.
\scs\ automatically computes certain supply chain metrics
such as the service level (proportion of demand satisfied)
and the average inventory level at a facility.

\scs\ was written because we (the authors) wished to analyze
the public-sector supply chain for medical drugs in Zambia.
The reader may wish to refer to our paper
\todo{Insert link to our MSOM paper.}
for an illustration of how \scs\
can be used in real-life to answer interesting research questions
related to inventory management.





\section{How to Navigate This Manual}

The logical structure of the supply chain simulated by \scs\
is described in \autoref{chapter:conceptual-model}.
The implementation of the logical structure in Java code
in described in \autoref{chapter:implementation}.
The simulation of a basic intermediate stocking supply chain
and the simulation of a basic cross-docking supply chain
are described in \autoref{chapter:tutorials}.

In \autoref{chapter:zambia},
we describe a real-world use case of \scs\
to evaluate the performance
of the public-sector supply chain for medical drugs in Zambia.
We present both the logical structure of the Zambia supply chain,
and the accompanying input data files.

Finally, installation instructions are found in
\autoref{chapter:installation}.


